Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-09-30 paper-2024-sac-marl-neighbouring-strategies.tex
add todonotes style

\usepackage{booktabs} % For formal tables

@@

\section{Introduction}
\begin{itemize}
\item Highlight the growing importance of MARL and its applications.
\item Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.
\item Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.
\item Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.
\item State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
\end{itemize}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{mytodonotes}

@@

\section{Introduction}

\gianlu{
Highlight the growing importance of MARL and its applications.

Discuss the challenges of MARL: non-stationarity, scalability, partial observability, and credit assignment.

Introduce the limitations of centralized training in MARL, specifically scalability issues and online learning challenges.

Present the motivation for exploring neighbor-based decentralized training strategies as a potential solution.

State the main objectives of the paper: to evaluate and compare the effectiveness of different neighbor-based methods and analyze their trade-offs.
}
